%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author : [Name] [Surname], Tomas Polasek (template)
% Description : First exercise in the Introduction to Game Development course.
%   It deals with an analysis of a selected title from the point of its genre, 
%   style, and mechanics.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,10pt,english]{article}

\usepackage[left=2.50cm,right=2.50cm,top=1.50cm,bottom=2.50cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

\newcommand{\ph}[1]{\textit{[#1]}}

\title{%
Analysis of Mechanics%
}
\author{%
Hai Phong Nguyen xnguye28%
}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

{%
\large

\begin{itemize}

\item[] \textbf{Title:} Rust

\item[] \textbf{Released:} 11.12.2013

\item[] \textbf{Author:} Facepunch Studios

\item[] \textbf{Primary Genre:} PvP Sandbox

\item[] \textbf{Secondary Genre:} Open World, First Person Shooter, Survival

\item[] \textbf{Style:} Realistic

\end{itemize}

}

\section*{\centering Analysis}
Rust is an open world, first person multiplayer game with survival elements. Players are placed in a vast island, in which they have to gather and use various resources to survive. The game is exclusively multiplayer and due to its mechanics, it encourages players to be hostile towards each other in order to obtain more resources and therefore gain a bigger advantage. Despite this, the sandbox character of the game offers players a freedom to choose their own objectives. The abundance of available items and mechanics gives players an opportunity to specialize in many different play-styles while keeping the high-stakes, tense essence thanks to the main focus on the Player vs Player part of the game.

Rust also expands the choice of play-styles by introducing various progression phases into its game-loop. Players first find themselves in the "primitive" phase, in which they must gather the most basic resources and watch out for dangerous wild animals. Players use primitive weapons, such as bows and spears, for combat. The "mid-game" phase introduces low tier guns and usually encourages players to battle each other for resources and fortify themselves in bases to protect their loot. In the "end-game", majority of players are fully equipped, and the focus shifts towards raiding the bases of other players.

Overall, this game fits fairly accurately in its main genre, PvP Sandbox, although some players may find this disappointing or frustrating, as some aspects from the secondary genres, such as survival elements, are often overshadowed or not so enjoyable by the main focus of the game. For example, the environmental hazards (wild animals controlled by AI, thirst and hunger, ...) are very basic and can be overcome very early into the game, leaving only the PvP as the tension creating aspect. 

\end{document}